\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-09 article.tex
Some notes

@@

\section{Linear Scan}
Another approach that also depends on liveness analysis is the linear scan algorithm.
It is a simple and efficient approach that performs a linear pass over IR to produce a register assignment significantly faster than all of the steps involved with graph coloring.
That said, it may be generate more imprecise assignments and therefore also be less performant at runtime, so the utility of such an approach depends on context.
As JIT compilation 
%Whether or not to  a cost depends on the context, as JIT compilation will often 
%reduced compile-time in  the fact that assignment is fast is a benefit in some cases.

The primary text is \textit{Linear Scan Register Allocation} \cite{linear}, the execution of which also relies on prior liveness analysis.

>>>>

The purpose is only to assign the same registers to different variables. You don't need to note down information about blocks etc.

@@

\section{Linear Scan}
Another approach that also depends on liveness analysis is the linear scan algorithm.
It is a simple and efficient approach that performs a linear pass over IR to produce a register assignment significantly faster than all of the steps involved with graph coloring.
That said, it may generate more imprecise assignments and therefore also be less performant at runtime, so the utility of such an approach depends on context.
Some compilers typically compile code into machine code ahead of time (AOT) while others depend on just-in-time (JIT) compilation which defers the compilation of code until runtime.
Therefore linear scan is an approach to register allocation that may be used to achieve reasonably performant runtime compilation.
%Whether or not to  a cost depends on the context, as JIT compilation will often 
%reduced compile-time in  the fact that assignment is fast is a benefit in some cases.

The primary text is \textit{Linear Scan Register Allocation} \cite{linear}, the application of which also relies on prior liveness analysis. Given liveranges, assignments are easily derived from only one pass through IR.
Similar to graph coloring, given \(K\) available GPRs, it must assign  as many variables as possible to these, and spill the remaining.
